Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-03 paper/main.tex
revision of intro and stimuli & procedure

\author{Christian~O.~Häusler\textsuperscript{1,2{*}}, Michael
Hanke\textsuperscript{1,2}}
% https://www.nature.com/sdata/publish/for-authors#other-formats

@@

\todo[inline]{Simon als Autor adden}

\todo[inline]{zweiten Satz: PPA ist die Region im ventral stream, die mehr auf
    static landscapes denn Gesichter reagiert. Ansonsten klingt es so, als ob
    PPA unabhängig von der Funktion definiert ist; dritte Satz ist irgendwie
    falsch konstruiert (narrative... audiovisual movie); ``significant increased
    activation in PPA'': PPA a priori durch localizer definiert? Oder ist der
    increase die Definition der PPA; Beschreibungen sind auf der einen seite
    sehr detailliert, aber der Vergleich mit dem localizer wird nicht explizit
erwähnt; Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
Localizer, oder? Das kommt bisher nur bedingt rüber}

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
The ``parahippocampal place area'' is classically considered to be a higher
visual area as increased hemodynamic activity in the PPA correlates/is
correlated with the perception of static pictures of landscapes (or landmarks)
compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
the audio-description of a Hollywood movie (i.e. the movie's soundtrack with an
additional narrator) the audio-visual movie can be used to isolate the PPA on a
group average level and in individual subjects.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) to build canonical general linear model (GLM) $t$-contrasts
and compare current results to results that we gained from a dedicated visual
localizer experiment conducted with the same 14 participants.
% compare to visual localizer experiment group results
On a group average level, our results show significantly increased activation in
the PPA but restricted to its anterior part [as well as in the retrosplenial and
lateral occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\todo{kinda bold statements; this depends on the data \&
discussion}\end{abstract}

@@

\todo[inline]{Den Start finde ich etwas komisch. "Cognitive neuroscientists use"
klingt sehr nach einer aktiven distanzierung}

\todo[inline]{Ich würde am Start definitiv kurz in die funktionelle
    Spezialisierung des visuellen Systems und die Organisation des ventralen
Streams einführen. Die kurze Darstellung der PPA ist dann aber gut}

\todo[inline]{ie "Kritik" an bisherigen PPA Studien finde ich insgesamt OK,
wobei nicht ganz klar wird, was genau das schlechte an "conceptualized" ist. Das
löst sich erst am Ende mit der "ecological validity" einigermaßen auf}

\todo[inline]{Aus meiner Sicht könnte die Motivation für die aktuelle Studie
    noch stärker werden. Du nennst zwar einige Schwächen, aber dann geht es sehr
    unvermittelt in Details der Studie. Meine Präferenz ist es eher, nochmal
    ganz klar zu sagen, warum es jetzt diese Studie braucht und was sie zum Feld
beitragen soll}

\todo[inline]{Damit zusammen hängend: Das Konzept der aktuellen Arbeit (place
information aus einem ongoing context zu verwenden) und warum das die Probleme
löst, würde ich auch noch etwas klarer darstellen. Du setzt zu viel voraus}

\todo[inline]{Das "then we analyzed publically available data" ist sehr
verwirrend, da es doch davor auch um StudyForest geht}

@@

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort. Cognitive neuroscientists use brain imaging
techniques to map perceptual and cognitive processes (e.g. seeing and
recognizing faces; \citep{kanwisher1997ffa}) to functional brain areas or
networks.
% What is the PPA?
A classic example of a higher-level visual area is the ``parahippocampal place
area'' (PPA) \citep{epstein1998ppa, epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus not anatomically but functionally
defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

\todo[inline]{The following review of O'Craven and Wolbers could be shortened.
Keeping the small paragraph regarding Aziz should make the focus on auditory
perception clearer. What do you think?}
% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality}.
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing famous faces and familiar places during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
[sighted] participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to haptically explored abstract geometric objects.
% Wolbers: connectivity analysis
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
    cortex, and compares connectivity during visual and haptic paradigm: ``The
    scene-related increase in coupling with the PPA was significantly stronger
    in multiple clusters in occipital cortex under visual than haptic
stimulation (Figure 2B; Table S2)''}

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
Nevertheless, the reviewed studies usually had three things in common.
% designed stimulus set
First, they employed a small sets of carefully chosen stimuli. Further, stimuli
were conceptualized to control confounding variables (e.g. color, luminance,
size, spatial frequencies, sentence length), a process that is often not
reported in detail.\todo{they usually just say ``we made the black \& white}
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed explicit perceptual judgment to keep participants
paying attention to the stimuli.
% averaging
Third, the reviewed studies averaged results across 7-11 subjects to improve
signal-to-noise ratio (SNR).
% disadvantages
Conceptualized stimuli, block-design experiments and the averaging approach have
their merits but also disadvantages.
% designed stimulus set
First, small sets of conceptualized stimuli presented on experimental blocks
poorly resembles our rich and multidimensional environment that our brains are
accommodated to [sonkusare2019naturalistic].
% block-design & task
Second, study participants can and will become aware about which perceptual
process is examined in the study by merely being exposed to the experimental
paradigm.
% inference: validity is poor
Thus, small sets of conceptualized stimuli and block-design experiment lack
external validity \citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage of averaging
Lastly, averaging data across subjects increases the SNR but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

% Open research question
In this study, we investigate if increased activation in the PPA correlates with
incidental ``spatial information'' in the audio-description of the Hollywood
movie ``Forrest Gump'' (i.e. the audio-only variant of the movie) and, for
cross-modal comparison, in the (actual) audio-visual movie (itself).
% we are different
Since we did not design the given naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews) for optimal localization performance of
the PPA, we operationalize the perception of landscapes and landmarks (compared
to e.g. faces and objects) differently from the reviewed studies.
% operationalization via annotation
Here, we annotated words spoken by the narrator of the audio-description as well
as cuts and depicted locations in the movie.
% public data
We then analyze publicly available data
(\href{http://www.studyforrest.org}{studyforrest.org}) from the same subjects
that listened to the audio-description and watched the movie during fMRI
scanning.
% first: group level AO
First, general linear model (GLM) contrasts based on the audio-description's
annotation are used to test if we could isolate the PPA with an auditory
stimulus on a group level.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to results based on the annotation of the movie.
% individual results
Lastly, focussing on the audio-description, we compare results on the level of
individual subjects to results of a block-designed visual localizer experiment
done with the same individuals \citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract, intro to
discussion and conclusion}
Our results demonstrate that (a), (b), (c).

@@

\todo[inline]{as mit dem "already used by" verwirrt eher}

\todo[inline]{Der StudyForest datansatz ist gut und knapp beschrieben. Die
Stimuli im VIS datensatz brauchen aber glaube ich etwas mehr erklärung}

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

\subsection{Stimuli}

\todo[inline]{merge Stimuli and ``Procedure'' (s. below)}

@@

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (matched in
luminance, size of 400 $\times$\unit[400]{px}) for each of six stimulus
categories: faces, bodies without heads, small objects, houses and
outdoor scenes comprising of nature and street scenes, and phase scrambled
images. Mirrored views of these 24 $\times$ 6 images were also used as stimuli.

@@

@@

% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

\subsection{Procedure}

\todo[inline]{Procedure (2.4.) ist nicht zwingend nötig bzw nicht als
separater Abschnitt}

% questionnaire
Participants filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

% VIS: presentation & instructions
In the VIS study, participants were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run, while they also
performed a one-back matching task to keep them attentive.

@@

\todo[inline]{Das mit den "five additional categories" habe ich nicht
    verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein.}

\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
annotierten events oder war das ein regressor der immer wieder kam?}

@@

% first level analysis
% regressors
% AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the
original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with movie cuts provided
by another previously published annotation \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AO analysis, we used all of the original 19
categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
time).
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories that served as experimental conditions
(see Table \ref{tab:ao-events}).
% setting beats other category
Events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``Jenny as a
teenager'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?}
%
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

\begin{table*}[t]
\caption{Overview of events to build the 18 regressors for the analysis of the
audio-only (AO) stimulus. Some of the annotation's original categories
    (female, females, fname; male, males, mname; face, head; object, objects;
    see Table\ref{tab:descr-nouns-rules})
    were pooled into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
    \texttt{fahead}; \texttt{object}).
\texttt{fg\_ad\_lrdiff} (left-right volume difference) and
\texttt{fg\_ad\_rms} (root mean square volume) represent one event for every movie frame (\unit[40]{ms}).
For a description of the five control conditions for movie cuts see Table \ref{tab:av-events}.}
\label{tab:ao-events}
\footnotesize
\begin{tabular}{lp{3.5cm}lllllllll}
\toprule

>>>>

\author{
    Christian~O.~Häusler\textsuperscript{1,2{*}},
    Simon B. Eickhoff\textsuperscript{1,2},
    Michael Hanke\textsuperscript{1,2}}
% https://www.nature.com/sdata/publish/for-authors#other-formats

@@

\todo[inline]{Clou der ganzen Geschichte ist doch: Man braucht keinen separaten
Localizer, oder? Das kommt bisher nur bedingt rüber; COH: well, if you also want
to have the ``visual part'' of the PPA then you need a visual paradigm}

\begin{abstract}
% < 170 words new analysis of existing data of interest to a broad section of
% our audience highlighting innovative examples of data reuse may be used to
% present compelling new findings & conclusions derived from published.  intro
Neuroimaging studies have parcellated the human brain into distinct functional
areas.
% PPA
A region in the human hippocampal cortex termed ``parahippocampal place area''
is classically considered to be a higher visual area as increased hemodynamic
activity in the PPA correlates with the perception of static pictures of
landscapes compared to pictures of faces or objects.
% What we do
In the current study, we exploratorily tested if spatial information embedded in
a Hollywood movie and its audio-description of (i.e. the movie's soundtrack with
an additional narrator) correlates with increased hemodynamic activity in the
PPA.
%
We use publicly available functional magnetic resonance imaging data
(studyforrest.org) to build canonical general linear model (GLM) $t$-contrasts
and compare current results to results that we gained from a dedicated visual
localizer experiment conducted with the same 14 participants.
% compare to visual localizer experiment group results
On a group average level, results of our whole brain analyses show
significantly increased activation restricted to the anterior part of the PPA
that was defined using the visual localizer [as well as in the retrosplenial
and lateral occipital cortex] of both hemispheres.
% individual results
On an individual level, results show significant bilateral clusters in the
anterior PPA of nine subjects and significant unilateral clusters in two
subjects.
% conclusion: generalizability
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of auditorily presented spatial
information.
% conclusion: PPA has subregions
Lastly, our results provides further evidence that the PPA can be divided into
functional subregions.\todo{kinda bold statements; this depends on the data \&
discussion}\end{abstract}

@@

@@

% brain mapping via fMRI
Humans can perceive and make sense of their daily environment casually and
seemingly without any effort.
%
Studies in the field of neuropsychology and neuroimaging (e.g.
\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different cognitive and perceptual
functions.
%%%%%%%%%%%%%%%%%%%%%% trenne diese Sätze %%%%%%%%%%%%%%5
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways of processing
different kind of visual information:
% dorsal vs ventral pathway
a dorsal pathway that leads into the parietal lob (the ``where pathway''), and a
ventral pathway that leads into into the temporal lobe (the ``what pathway'')
\citep{goodale1992separat, mishkin1982contribution}.
%
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}, and thus is not anatomically but
functionally defined:
% neural correlate of scene perception
increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
tools or faces) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

\todo[inline]{The following review of O'Craven and Wolbers could be shortened.
Keeping the small paragraph regarding Aziz should make the focus on auditory
perception clearer. What do you think?}

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental} and haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality} whereas a study using
spoken sentences yielded mixed results \citep{aziz2008modulation}.
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing famous faces and familiar places during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
[sighted] participants showed increased activation during a delayed
match-to-sample task of haptically explored scenes constructed from LEGO bricks
compared to haptically explored abstract geometric objects.
% Wolbers: connectivity analysis
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
    cortex, and compares connectivity during visual and haptic paradigm: ``The
    scene-related increase in coupling with the PPA was significantly stronger
    in multiple clusters in occipital cortex under visual than haptic
stimulation (Figure 2B; Table S2)''}

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
The reviewed studies usually had three things in common that come along with
advantages but also disadvantages:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-designed paradigms to maximize detection power.
Further, they usually employed an explicit perceptual judgment task.
%
Block-design studies that use conceptualized stimuli and a task have the
advantages of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% disandvantage of stimuli and block
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of a[n
explicit] perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Lastly, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approch improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

\todo[inline]{SE: make motivation of study clearer; gap in research; how it
    (might) adance(s) the field; make clearer how current study solves the
    problem; COH: I revised this part, it's clearer at least
if I read it now}

% Open research question
In this study, we investigate if increased hemodynamic activity in the PPA
correlates with ``spatial information'' presented under more ecologically valid
conditions.
% we are different We used two naturalistic
Therefore, we annotated perceptual information embedded in two [perceptual]
rich/multidimensional and continuous naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews):
% audio-description
a) the audio-description of the Hollywood movie ``Forrest Gump'' (i.e. the
audio-only variant of the movie), and
% audio-visual
b) the [actual] audio-visual movie [itself].
% studyforrest dataset
We then analyzed corresponding fMRI data from the same subjects that listened
to the audio-description and watched the audio-visual movie as part of the
publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}).
% first: group level AO
First on a group average level, general linear model (GLM) contrasts based on
the audio-description's annotation are used to test if spatial information
embedded in an exclusively auditory stimulus correlates with increased
hemodynamic activity in the PPA that we defined using a block-designed visual
localizer experiment done with the same subjects \citep{sengupta2016extension}.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to GLM results based on the annotation of the movie.
% individual results
Lastly on the level of individual subjects and focussing on the
audio-description [as a possible substitute for a visual localizer], we compare
results of the naturalistic stimuli to results of the visual localizer
\citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract, intro to
discussion and conclusion} Our results demonstrate that (a), (b), (c).

@@

% intro
We used three subdatasets of the publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}) that has already been
used by other research groups for independent research questions
(e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'',
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), and
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}).
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

\subsection{Stimuli and Procedure}

@@

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).
% procedure: questionnaire
Subjects filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AO & AV: instructions
Before the experiment, participants were instructed to inhibit physical
movements except for eye-movements, and otherwise to simply ``enjoy the
audiobook'' or ``enjoy the movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

\todo[inline]{contrary to claims in Sengupta, the pictures are NOT the same
as used in Haxby, 2011; sets might have an intersection though}

% VIS study picture categories
All stimuli of the VIS study were already used in a previous study
\citep{haxby2011common}. There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) ) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% mirror images
Mirrored views of these 24 $\times$ 6 images were also used as stimuli.
% controlled luminance and size
Images were matched in luminance and size of 400 $\times$\unit[400]{px}
(displayed at a size of approximately
\unit[10]{$^{\circ}$}$\times$\unit[10]{$^{\circ}$} visual angle.
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

\todo[inline]{Ich würde abschnitt 2.8 (statistical analysis) teilen:
    a) die regressors, die dann mit der beschreibung der annotation kombinieren
    b) die eigentliche statistik)}

@@

%
Since we did not design the given naturalistic stimuli for optimal localization
performance of the PPA, we operationalized the perception of landscapes and
landmarks (compared to e.g. faces and objects) by annotating words spoken by the
narrator of the audio-description as well as cuts and depicted locations in the
movie.
% todo stimuli were not designed for research purposes
Both natural stimuli were not design to isolate a specific brain area but to
entertain their audiences free from any perceptual or behavioral task.
% fixed stimuli and operationalization
We annotated the temporal structure of the fixed stimuls material to
operationalize the perception of different stimulus features (e.g. the
perception of landmarks and faces) and create GLM contrasts in the subsequent
data analysis.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``in Greenbow'', ``in a
disco'', ``the platoon wades through a rice field''). They also comprise words
that could count as a member of another categories in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``Jenny as a
teenager'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

@@

@@

@@

\subsubsection{Annotation of naturalistic stimuli}

\subsubsection{Regressors}

% first level analysis regressors AO: events
For the analysis of the AO stimulus, we created regressors correlating with the
occurrence of descriptive nouns spoken by the narrator that were added to the
original annotation of speech \citep{haeusler2020speechanno}.
% AV events
For the AV stimulus, we created regressors correlating with movie cuts provided
by another previously published annotation \citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}

% procedure
Both annotations were split into eight parts corresponding to the eight stimulus
segments.
% AO events
To create regressors for the AO analysis, we used all of the original 19
categories of descriptive nouns except ``\texttt{++}'' (i.e. cues regarding
time).
% pooling
Some categories that were similar but offered only a small amount of counts were
pooled resulting in eleven new categories that served as experimental conditions
(see Table \ref{tab:ao-events}).
% setting beats other category
Events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``Jenny as a
teenager'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.

\todo[inline]{Gab es ein separates null-event für jeden zeitraum zwischen zwei
annotierten events oder war das ein regressor der immer wieder kam?}
% null regressors
If a segment did not contain an event of a category, a null regressor was chosen
for that category in that segment.\todo{wenn ich "null regressor" nehme, darf
ich den ganzen Run, glaube ich, in der 2nd level Analyse gar nicht benutzen?
Hatte, glaube ich, Jeanette Mumford in einem ihren Videos mal gesagt}

\todo[inline]{Das mit den "five additional categories" habe ich nicht
verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein.}
% categories taken from movie cut annotation
Five additional categories were created from the annotation of movie cuts and
modeled as impulse events to capture variance of a possibly confounding change
of the soundscape after a cut, and to create contrasts of cross-modal negative
control (see details below).
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?}
%
Lastly, we used continuous bins of information about two auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% Reference to table
An explanation and counts of the eleven speech-related event categories, the
five movie cut-related categories, and the two low-level confounds can be found
in Table \ref{tab:ao-events}.

\begin{table*}[t] \caption{Overview of events to build the 18 regressors for the
        analysis of the audio-only (AO) stimulus. Some of the annotation's
        original categories (female, females, fname; male, males, mname; face,
        head; object, objects; see Table\ref{tab:descr-nouns-rules}) were pooled
        into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
        \texttt{fahead}; \texttt{object}).  \texttt{fg\_ad\_lrdiff} (left-right
        volume difference) and \texttt{fg\_ad\_rms} (root mean square volume)
